### 2014-06-06 method.tex
added ross' design choices table
adding histogram of # regions per image
results table and figures
Explained the cascaded-CNN a bit more

Table ??? shows mAP performance on PASCAL VOC 2007 test for these various choices.
The best configuration, in terms of mAP, uses a 7 level pyramid, a warp size of $7 \times 7$ with bilinear interpolation, and max pooling.
The first level of our pyramid is computed from a $1713 \times 1713$ pixel image, which yields a $108 \times 108$ cell feature map.
The gold standard (non-pyramid) R-CNN performance using the same non-fine-tuned CNN is 44.2\% mAP.
Our best result with Pyramid R-CNN is slightly worse, at 41.9\%.

@@

@@

Most ROIs that go through the CNN in R-CNN do not contain objects of interest, and are simply background.
It would be useful to quickly reject these regions, without expending the full amount of computation on them.

The Cascaded CNN, shown in \autoref{fig:ccnn}, augments the CNN network with an ``Early Terminate'' option: after some layers, the network decides whether to keep computing the input with the next layer, or to terminate with a classification.
For our purpose, the terminate layers are trained to separate Background/Foreground, terminating if they are confident that the input is Background.
Only the last classification layer output the full multi-class scores.

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.98\columnwidth]{figures/ccnn.pdf}
\caption{
The Cascaded CNN has a reject option after certain layers.
\todo{Redo figure to introduce the Reject layers and color their arrows red to make it clear that a choice is being made.}
}\label{fig:ccnn}
\end{center}
\end{figure}

@@

>>>>

\autoref{tab:prcnn} shows mAP performance on PASCAL VOC 2007 test for these various choices.
The best configuration, in terms of mAP, uses a 7 level pyramid, a warp size of $7 \times 7$ with bilinear interpolation, and max pooling.
The first level of our pyramid is computed from a $1713 \times 1713$ pixel image, which yields a $108 \times 108$ cell feature map.
The gold standard (non-pyramid) R-CNN performance using the same non-fine-tuned CNN is 44.2\% mAP.
Our best result with Pyramid R-CNN is slightly worse, at 41.9\%.

@@

\begin{table}[ht]
\caption{
    Pyramid R-CNN design choices.
}\label{tab:prcnn}
\input{pyra_rcnn_table}
\end{table}

@@

Most ROIs that go through the CNN in R-CNN do not contain objects of interest, and are simply background.
It would be useful to quickly reject these regions, without expending the full amount of computation on them. Since most of the time is spend in the convolution layers, we introduce a reject layer after pool1, pool2, conv3 and conv4, this allows skipping the computation of the following convolutions. These reject layers were trained using the corresponding fine-tuned CNN.

The Cascaded CNN, shown in \autoref{fig:ccnn}, augments the CNN network with an ``Early Reject'' option: after some layers, the network decides whether to keep computing the input with the next layer, or to reject the region since it is background.
For our purpose, the reject layers are trained to separate Background/Foreground, terminating if they are confident that the input is Background. The last classification layer still outputs the full multi-class scores for the surviving regions.

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.98\columnwidth]{figures/ccnn.pdf}
\caption{
The Cascaded CNN has a reject option after pool1, pool2, conv3 and conv4 layers.
\todo{Redo figure to introduce the Reject layers and color their arrows red to make it clear that a choice is being made.}
}\label{fig:ccnn}
\end{center}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.5\linewidth]{figures/roi_hist.pdf}
\caption{
    Distribution of the number regions per image on PASCAL VOC2007 validation set.
}\label{fig:roi_hist}
\end{figure}

\begin{table}[ht]
\centering
\caption{
Full table of AP vs. Time results on PASCAL VOC 2007.
}\label{tab:results}
\include{results_table}
\end{table}

\begin{figure}[ht]
\centering
\includegraphics[width=0.5\linewidth]{figures/_speedup.pdf}
\caption{
Speedup.
}\label{fig:speedup}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics[width=0.5\linewidth]{figures/_all_selected.pdf}
\caption{
AP vs. Time plots.
}\label{fig:apvst}
\end{figure}
